### 2012-02-13 exam3/1.tex
Add dir problem.

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 18\\ \hline
2 & & 10\\ \hline
3 & & 15\\ \hline
4 & & 18\\ \hline
%5 & & 5\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 61+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

>>>>

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 18\\ \hline
2 & & 10\\ \hline
3 & & 15\\ \hline
4 & & 15\\ \hline
5 & & 18\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 76+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

Here are data and class definitions for representing the files and
directories of a computer:

\begin{verbatim}
;; An Elem is one of
;; - (new file% String Number)
;; - (new dir% String LoElem)
(define-class file% (fields name size))
(define-class dir% (fields name elems))

;; A LoElem is one of
;; - (new mt%)
;; - (new cons% Elem LoElem)
(define-class mt%)
(define-class cons% (fields first rest))    
\end{verbatim}

\noindent
Here is an example of a directory tree and its representation as an
\verb|Elem|:
\begin{verbatim}
#|
 User
   +-- A
   |   +-- a.txt
   |   +-- B
   |       +-- b.rkt
   +-- C
       +-- c.c
|#

(define mt (new mt%))
(define a (new file% "a.txt" 5))
(define b (new file% "b.rkt" 10))
(define c (new file% "c.c" 1000))

(define C/ (new dir% "C" (new cons% c mt)))
(define B/ (new dir% "B" (new cons% b mt)))
(define A/ (new dir% "A" (new cons% a (new cons% B/ mt))))
(define User/ (new dir% "/" (new cons% A/ (new cons% C/ mt))))
\end{verbatim}

\newpage
\noindent
Your job is to implement one of the main tasks of the common Unix
utility \verb|find|, which gives a list of all the files within an
element.  To do so, add a \verb|list-files| method of \verb|Elem|
which produces a list of files.  So for example, we expect:
\begin{verbatim}
(check-expect (User/ . list-files) 
              (new cons% a (new cons% b (new cons% c mt))))
\end{verbatim}
\emph{Hint}: it may come in handy to be able to concatenate two
\verb|LoElem| together.

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\fi

\begin{solution}
\begin{verbatim}
;;> [1pts -- interfaces, contracts, purpose]
;; An Elem implements
;; - list-files : -> LoElem
;;   List all files within this element.

;;> [2pts -- interfaces, contracts, purpose]
;; A LoElem implements
;; - list-files : -> LoElem
;;   List all files within this list of elements.
;; - append : LoElem -> LoElem
;;   Append this list of elements to given list.

;;> [1pt -- code]
;; in dir%
(define (list-files)
  (this . elems . list-files))

;;> [1pt -- code]
;; in file%
(define (list-files)
  (new cons% this (new mt%)))

;;> [2pt -- code]
;; in mt%
(define (append loe) loe)
(define (list-files) this)

;;> [4pt -- code]
;; in cons%
(define (append loe)
  (new cons% (this . first) (this . rest . append loe)))
(define (list-files)
  (this . first . list-files . append (this . rest . list-files)))

;;> [1pt -- sanity]

;;> [3pts -- tests]
;; tests
(check-expect (mt . append (new cons% a mt)) (new cons% a mt))
(check-expect ((new cons% a mt) . append (new cons% b mt))
              (new cons% a (new cons% b mt)))

(check-expect (mt . list-files) mt)
(check-expect ((new cons% a (new cons% b mt)) . list-files)
              (new cons% a (new cons% b mt)))

(check-expect (a . list-files) (new cons% a mt))
\end{verbatim}
\end{solution}

\end{problem}
\newpage
